### 2022-08-13 doc/src/IOMMU.tex
Instruction REV8 is added by extension Zbb

\begin{commentary}
Big-endian-configured harts that make use of MRIFs are expected to
implement the REV8 byte-reversal instruction defined by the {\RISCV}
``Bitmanip'' extension (B~extension), or pay the cost of endianness
conversion using a sequence of instructions.
\end{commentary}

>>>>

\begin{commentary}
Big-endian-configured harts that make use of MRIFs are expected to
implement the REV8 byte-reversal instruction defined by
standard {\RISCV} extension Zbb, or pay the cost of endianness
conversion using a sequence of instructions.
\end{commentary}
